A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2023-07-20 manuscript/manuscript.Rmd
video playlist provided
minor edits

This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

@@

@@

>>>>

We thank Ms Megan Soria (Deakin University) for discussions on the concept and manuscript.
This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

@@

* Instructional video guides are available on YouTube: https://www.youtube.com/playlist?list=PLAAydBPtqFMXDpLa796q7f7W1HK4t_6Db

@@

* The code repository and Docker image have been uploaded to Zenodo for lon-term archiving and are available from: [TBA].
